quollr: An R Package for Visualizing 2D Models from Nonlinear Dimension Reductions in High Dimensional Space

### 2024-03-30 paper-quollr.Rmd
Add the steps to write about hexagonal binning

<!-- add about main function to gen 2D and highD models-->
## Constructing the 2D model

<!--Discuss the model can be generated with bin centroids or bin means-->

@@

<!-- add about main function for hexagonal bining-->

>>>>

The mains steps for the algorithm can be executed by the main function `fit_highd_model()`, or can be run separately for more flexibility. When constructing the 2D model, the user can choose either to fir the 2D model with hexagonal bin centroids or bin means using `is_bin_centroid` argument.

<!-- add about main function to gen 2D and highD models-->
<!--Discuss the model can be generated with bin centroids or bin means-->

## Constructing the 2D model

@@

The mains steps for the hexagonal binning algorithm can be executed by the main function `hex_binning()`, or can be run separately for more flexibility.
<!-- add about main function for hexagonal bining-->

**Step 1: Compute hexagonal grid configurations**

**Step 2: Generate the hexagonal bin centroids**

**Step 3: Create the hexagonal grid**

**Step 4: Assign NLDR data to hexagons**

### 2024-03-30 paper-quollr.tex
Add the steps to write about hexagonal binning

@@

>>>>

The mains steps for the algorithm can be executed by the main function \texttt{fit\_highd\_model()}, or can be run separately for more flexibility. When constructing the 2D model, the user can choose either to fir the 2D model with hexagonal bin centroids or bin means using \texttt{is\_bin\_centroid} argument.

@@

The mains steps for the hexagonal binning algorithm can be executed by the main function \texttt{hex\_binning()}, or can be run separately for more flexibility.

\textbf{Step 1: Compute hexagonal grid configurations}

\textbf{Step 2: Generate the hexagonal bin centroids}

\textbf{Step 3: Create the hexagonal grid}

\textbf{Step 4: Assign NLDR data to hexagons}
